Identifying Software Performance Changes Across Variants and Versions

### 2020-08-07 paper.tex
incorporated minor issues from reviewer 1

	As the distribution in Figure~\ref{fig:results_rq1_frequency} illustrates, most experiments terminated after the minimum of three iterations or with less than 29 iterations. That is, most experiments reached our termination criterion. 
	Regarding the The measurement effort, for small systems with 8 configuration options, we required up to 50~\% of all possible measurements. By contrast, for greater systems, the required measurement effort was well below 1~\%. The high reported measurement effort for systems with 8 configuration options is due to our choice of the measurements per iterations, which vastly over-approximates. Since we are able handle systems with more configuration options with similar effort, we are confident, that a smaller number of measurements per iteration would reduce the relative measurement effort required substantially.

@@

	For \textsc{xz}, the commit messages for both change points referenced three particular configuration options (\textsf{hc3}, \textsf{hc4}, \textsf{MatchFinder}). For \textsc{lrzip}, one commit message references a configuration option (\textsf{zpac}). Four of seven commit messages contained keywords relating to a performance. Two examples are the following:

@@

	We attribute the inconclusive results for \textsc{lrzip} in part to the inconsistency. In addition, for both \textsc{xz} and \textsc{lrzip}, many configuration options are „alternatives“, i.e., for a functionality, such as the compression algorithm, only one of the available options can be selected. In our approach, we employ Lasso regression for automated feature selection. This regression model might, given only a small configuration sample, have difficulties with attributing a change point to multiple alternative configuration options and rather opt for one instead.  Across the repetitions of our experiments, we have found candidate solutions close to the two change points commits for \textsc{xz} and \textsc{oggenc}, respectively, on average, after 3 to 5 iterations. After more than five iterations, the majority of repetitions pinpointed commits correctly within our narrow 5 commit interval.
	\vspace{2mm}
	\greybox{
		\textbf{Summary}: Our approach is able to precisely link change points to commits with real-world data. Manually associating commits with configuration options worked in many cases as the automated analysis was inconclusive due to incomplete data in the repositories. We observed, at least, one inconsistency in the configuration interface of one system.
	}

>>>>

	As the distribution in Figure~\ref{fig:results_rq1_frequency} illustrates, most experiments terminated after the minimum of three iterations or with less than 29 iterations. That is, most experiments reached our termination criterion. 
	Regarding the measurement effort, for small systems with 8 configuration options, we required up to 50~\% of all possible measurements. By contrast, for greater systems, the required measurement effort was well below 1~\%. The high reported measurement effort for systems with 8 configuration options is due to our choice of the measurements per iterations, which vastly over-approximates. Since we are able handle systems with more configuration options with similar effort, we are confident, that a smaller number of measurements per iteration would reduce the relative measurement effort required substantially.

@@

	For \textsc{xz}, the commit messages for both change points referenced three particular configuration options (\textsf{hc3}, \textsf{hc4}, \textsf{MatchFinder}). For \textsc{lrzip}, one commit message references a configuration option (\textsf{zpac}). Four of seven commit messages contained keywords relating to performance. Two examples are the following:

@@

	We attribute the inconclusive results for \textsc{lrzip} in part to the inconsistency. In addition, for both \textsc{xz} and \textsc{lrzip}, many configuration options are "alternatives", i.e., for a functionality, such as the compression algorithm, only one of the available options can be selected. In our approach, we employ Lasso regression for automated feature selection. This regression model might, given only a small configuration sample, have difficulties with attributing a change point to multiple alternative configuration options and rather opt for one instead.  %Across the repetitions of our experiments, we have found candidate solutions close to the two change points commits for \textsc{xz} and \textsc{oggenc}, respectively, on average, after 3 to 5 iterations. After more than five iterations, the majority of repetitions pinpointed commits correctly within our narrow 5 commit interval.
	\vspace{2mm}
	\greybox{
		\textbf{Summary}: Our approach is able to precisely link change points to commits with real-world data. Manually associating commits with configuration options worked in many cases as the automated analysis was inconclusive due to incomplete data in the repositories. We observed, at least, one inconsistency in the configuration interface of one system.
	}
